Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian

### 2023-02-17 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Added random-effects for presidents' party ideology

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  word_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  pdf_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem. We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches. To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985. We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
---

@@

```{r odds ratio, fig.cap = "Odds-ratio and confidence intervals for fixed-effects logistic regressions indexed by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=FALSE, results="asis"}

ci1 <- exp(confint(c1))
ci2 <- exp(confint(c2))
ci3 <- exp(confint(c3))
ci4 <- exp(confint(c4))
ci5 <- exp(confint(c5))

stargazer::stargazer(c5, c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Odds-ratio for fixed-effects logistic regressions indexed by president",
                     ci = T, apply.coef = exp,
                     ci.custom = list(ci5, ci1, ci2, ci3, ci4, ci5),
                     t.auto=F, p.auto=F,
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                         "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Election Year"))
```

```{r presid set, fig.cap="Random-effects logistic regressions for seeting and president indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

ama_model_lag$president <- factor(ama_model_lag$president,
                                  levels = c("Sarney", "Collor", "Itamar", "FHC",
                                             "Lula", "Dilma", "Temer", "Bolsonaro"))
ama_model2_lag$president <- factor(ama_model2_lag$president,
                                   levels = c("Sarney", "Collor", "Itamar", "FHC",
                                              "Lula", "Dilma", "Temer", "Bolsonaro"))
ps1 <- plm(con_vs_all ~ as.factor(location_cat) + as.factor(president),
                         data = ama_model_lag,
                         model = "random", index = "year")
ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + as.factor(president),
                         data = ama_model_lag,
                         model = "random", index = "year")
ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + as.factor(president),
                         data = ama_model_lag,
                         model = "random", index = "year")
ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + as.factor(president),
                         data = ama_model_lag,
                         model = "random", index = "year")
ps5 <- plm(amazon_speech ~ as.factor(location_cat) + as.factor(president),
                         data = ama_model2_lag,
                         model = "random", index = "year")

stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
                     title = "Random-effects logistic regressions for settings and president indexed by year",
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                         "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "Franco", "Collor", "Cardoso", "Lula",
                                          "Rousseff", "Temer", "Bolsonaro"))
```

>>>>

---
title: "Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian
  Presidential Discourse since 1985"
author:
- "Livio Silva-Muller"
- Henrique Sposito^[Both authors contributed equally to the article. Names are ordered
  alphabetically. Livio is a PhD Candidate in Sociology and affiliated to the Albert
  Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations
  and Political Sciences and affiliated to the Centre for International Environmental
  Studies.]
date: "17 February 2023"
output:
  pdf_document: default
  latex_engine: xelatex
  fig_caption: yes
  html_document:
    df_print: paged
  word_document: default
fontsize: 12pt
mainfont: Times New Roman
header-includes:
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- |
  \providecommand{\keywords}[1]{\textbf{Keywords:} #1}
  \providecommand{\wordcount}[1]{\textbf{Word Count:}#1}
always_allow_html: yes
bibliography: references.bib
csl: chicago.csl
abstract: The Amazon is a complex object of policy that comprises environmental, economic, social, and sovereignty concerns. Despite this complexity, governments are often portrayed as having a single understanding of the Amazon as a political problem. We investigate how the Amazon has been constructed as a problem in Brazilian presidential speeches. To do so, we develop a framework that accounts for how important actors in transnational politics, as presidents, construct policy objects as particular problems depending on where and when they participate in politics. Using supervised machine learning, we classify statements about the Amazon in 6240 presidential speeches since 1985. We find that Brazilian presidents often construct the Amazon as an environmental problem when speaking far away from the region, whereas they usually construct it as problems of economic integration or social development when in the Amazon. Furthermore, presidents increasingly construct the Amazon as multiple problems rather than a dichotomy between economic or environmental problems.
---

@@

```{r presid set, fig.cap="Random-effects logistic regressions for setting and presidents' party ideology indexed by year", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

left_right_VDEM <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/V-Dem-CPD-Party-V2.rds") %>% 
  dplyr::filter(country_name == "Brazil", 
                year >= 1985) %>%
  dplyr::select(year, v2pashname, v2pariglef) %>%
  tidyr::drop_na() %>%
  dplyr::rename(party = v2pashname) %>%
  group_by(party) %>%
  summarise(left_right = mean(v2pariglef))

ama_model_lag <- dplyr::left_join(ama_model_lag, left_right_VDEM, by = "party")
ama_model2_lag <- dplyr::left_join(ama_model2_lag, left_right_VDEM, by = "party")

ps1 <- plm(con_vs_all ~ as.factor(location_cat) + left_right,
                         data = ama_model_lag,
                         model = "random", index = "year")
ps2 <- plm(EI_vs_all ~ as.factor(location_cat) + left_right,
                         data = ama_model_lag,
                         model = "random", index = "year")
ps3 <- plm(SD_vs_all ~ as.factor(location_cat) + left_right,
                         data = ama_model_lag,
                         model = "random", index = "year")
ps4 <- plm(sov_vs_all ~ as.factor(location_cat) + left_right,
                         data = ama_model_lag,
                         model = "random", index = "year")
ps5 <- plm(amazon_speech ~ as.factor(location_cat) + left_right,
                         data = ama_model2_lag,
                         model = "random", index = "year")

stargazer::stargazer(ps5, ps1, ps2, ps3, ps4, digits = 3, no.space = TRUE,
                     title = "Random-effects logistic regressions for setting and presidents' party ideology indexed by year",
                      column.sep.width = "-12pt",
                      font.size="small",
                      dep.var.labels = c("Amazon Speech",
                                         "Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty"),
                     covariate.labels = c("Amazonian Countries",
                                          "Non Amazonian States",
                                          "Non Amazonian Countries",
                                          "President's party left-right scale (VDEM)"))
```
